---
title: "SAD tobacco Xylella"
author: "Emerson"
date: "4/10/2020"
output: html_document
editor_options: 
  chunk_output_type: inline
---

```{r setup, include=FALSE}
library(gsheet)
library(tidyverse)
library(ggridges)

library(lme4)
library(gtools)
library(sjmisc)
library(ggsci)
```


```{r}
sad1 <- gsheet2tbl("https://docs.google.com/spreadsheets/d/19CqDqgWF1dGFXZHCdPMWUi9D1Fhd39elrYN7-MEwoAI/edit?usp=sharing")

sad1 <- sad1 %>%
  mutate(Aided2 = as.numeric(Aided2)) %>%
  filter(!Leaf %in% c(47, 15, 43, 14, 38, 4, 24, 9, 44, 29)) %>%
  mutate(true = rowMeans(x = select(
    .data = .,
    4:6
  )))
```




```{r}
summary(sad1$ImageJ)
summary(sad1$LeafDoctor)
summary(sad1$Assess)
sd(sad1$ImageJ)
sd(sad1$LeafDoctor)
sd(sad1$Assess)

sad11 <- sad1 %>%
  dplyr::select(-9) %>%
  mutate(Aided = as.numeric(Aided)) %>%
  pivot_longer(4:7,9,
    names_to = "Method",
    values_to = "Measure"
  )
```



## Software measures

### Figure 1




```{r}
p_ASLD <- sad11 %>%
  ggplot(aes(Assess, LeafDoctor)) +
  geom_point(size = 3, shape = 1) +
  geom_abline(slope = 1, intercept = 0) +
  coord_fixed() +
  labs(
    x = "APS Assess (%)",
    y = "Leaf Doctor (%)"
  )

p_ASIJ <- sad11 %>%

  ggplot(aes(Assess, ImageJ)) +
  geom_point(size = 3, shape = 1) +
  coord_fixed() +
  geom_abline(slope = 1, intercept = 0) +
  labs(
    x = "APS Assess (%)",
    y = "ImageJ (%)"
  )

p_IJLD <- sad11 %>%
  ggplot(aes(ImageJ, LeafDoctor)) +
  geom_point(size = 3, shape = 1) +
  coord_fixed() +
  geom_abline(slope = 1, intercept = 0) +
  labs(
    x = "ImageJ (%)",
    y = "Leaf Doctor (%)"
  )


sad11 <- sad1 %>%
  select(3:6, 10) %>%
  unique()

p_trueLD <- sad11 %>%
  ggplot(aes(true, (LeafDoctor - true))) +
  geom_point(shape =1, size =3) +
  geom_hline(yintercept = 0) +
  ylim(-4,4)+
  labs(
    x = "Mean software measures (%)",
    y = "Leaf Doctor measure (%)")

p_trueAS <- sad11 %>%

  ggplot(aes(true, (Assess - true))) +
  geom_point(shape =1, size =3 ) +
  geom_hline(yintercept = 0)+
    ylim(-4,4)+
  labs(
    x = "Mean software measure (%)",
    y = "Assess measure (%)")

p_trueIJ <- sad11 %>%
  ggplot(aes(true, (ImageJ - true))) +
  geom_point(shape = 1, size =3) +
  geom_hline(yintercept = 0)+
    ylim(-4,4)+
    labs(
    x = "Mean software measure (%)",
    y = "ImageJ measure (%)")

library(patchwork)
soft2 <- (p_trueAS | p_trueIJ | p_trueLD) 


soft1 <- (p_ASLD | p_ASIJ | p_IJLD)

(soft1 / soft2) + plot_annotation(tag_levels = "A")  
ggsave("figs/fig_softwares.png", width = 9, height = 7)
```

### CCC software measures

```{r}
library(epiR)
epi.ccc(sad11$true, sad11$ImageJ)
epi.ccc(sad11$true, sad11$LeafDoctor)
epi.ccc(sad11$true, sad11$Assess)


sad12 <- sad1 %>%
  select(7, 8, 10) %>%
  unique()
epi.ccc(sad12$Aided, sad12$true)

epi.ccc(sad12$Unaided, sad12$true)

```



```{r fig.height=8, fig.width=4}
library(cowplot)
Fig1A <- sad1 %>%
  select(1:3, 7:10) %>%
  ggplot(aes(true, (Unaided - true))) +
  geom_jitter(
    shape = 16, alpha = .5, width = .5, height = 0.2,
    color = "darkred", size = 2
  ) +
  geom_smooth(se = F, size = 2, linetype = 1, color = "grey50") +
  # geom_boxplot(notch=FALSE, outlier.colour = NA)+
  theme_minimal_grid() +
  xlim(0, 85) +

  ylim(-50, 75) +
  labs(x = "Percent actual severity", y = "Percent point error") +
  #  facet_wrap(~Rater, ncol = 7)+
  geom_abline(intercept = 0, slope = 0)

Fig1B <- sad1 %>%
  select(1:3, 7:10) %>%
  ggplot(aes(true, (Aided - true))) +
  geom_jitter(
    shape = 16, alpha = .5, width = .5, height = 0.2,
    color = "steelblue", size = 2
  ) +
  geom_smooth(se = F, size = 2, linetype = 1, color = "grey50") +
  theme_minimal_grid() +

  xlim(0, 85) +
  ylim(-50, 75) +
  labs(x = "Percent actual severity", y = "Percent point error") +
  # facet_wrap(~Rater, ncol = 5)+
  geom_abline(intercept = 0, slope = 0)

library(patchwork)
Fig1 <- (Fig1A | Fig1B) + plot_annotation(tag_levels = "A")
ggsave("figs/fig1.png", width = 8, height =4)
```






```{r fig.height=8, fig.width=4}
sad1 %>%
  select(1:3, 7:10) %>%
  ggplot(aes(true, (as.numeric(Aided2) - true), color = Laboratory)) +
  geom_point(shape = 1) +
  theme_minimal() +
  facet_wrap(~Laboratory, ncol = 1) +
  geom_abline(intercept = 0, slope = 0)
```



## epiR

```{r}
library(epiR)
dat_ccc <- sad1 %>%
  pivot_longer(7:8, names_to = "type", values_to = "sev") %>%
  group_by(type, Laboratory, Rater) %>%
  summarise(
    ccc_est = epi.ccc(ImageJ, sev)$rho.c$est,
    ccc_lower = epi.ccc(ImageJ, sev)$rho.c$lower,
    ccc_upper = epi.ccc(ImageJ, sev)$rho.c$upper,
    cb = epi.ccc(ImageJ, sev)$C.b,
    lshift = epi.ccc(ImageJ, sev)$l.shift,
    sshift = epi.ccc(ImageJ, sev)$s.shift,
    r = cor(ImageJ, sev)
  ) %>%
  mutate(time = case_when(
    type == "Unaided" ~ 1,
    TRUE ~ 2
  ))

library(epiR)

dat_ccc_assess <- sad1 %>%
  pivot_longer(7:8, names_to = "type", values_to = "sev") %>%
  group_by(type, Laboratory, Rater) %>%
  summarise(
    ccc_est = epi.ccc(Assess, sev)$rho.c$est,
    ccc_lower = epi.ccc(Assess, sev)$rho.c$lower,
    ccc_upper = epi.ccc(Assess, sev)$rho.c$upper,
    cb = epi.ccc(Assess, sev)$C.b,
    lshift = epi.ccc(Assess, sev)$l.shift,
    sshift = epi.ccc(Assess, sev)$s.shift,
    r = cor(Assess, sev)
  )


dat_ccc_leaf <- sad1 %>%
  pivot_longer(7:8, names_to = "type", values_to = "sev") %>%
  group_by(type, Laboratory, Rater) %>%
  summarise(
    ccc_est = epi.ccc(LeafDoctor, sev)$rho.c$est,
    ccc_lower = epi.ccc(LeafDoctor, sev)$rho.c$lower,
    ccc_upper = epi.ccc(LeafDoctor, sev)$rho.c$upper,
    cb = epi.ccc(LeafDoctor, sev)$C.b,
    lshift = epi.ccc(LeafDoctor, sev)$l.shift,
    sshift = epi.ccc(LeafDoctor, sev)$s.shift,
    r = cor(LeafDoctor, sev)
  )

dat_ccc_true <- sad1 %>%
  pivot_longer(7:8, names_to = "type", values_to = "sev") %>%
  group_by(type, Laboratory, Rater) %>%
  summarise(
    ccc_est = epi.ccc(true, sev)$rho.c$est,
    ccc_lower = epi.ccc(true, sev)$rho.c$lower,
    ccc_upper = epi.ccc(true, sev)$rho.c$upper,
    cb = epi.ccc(true, sev)$C.b,
    lshift = epi.ccc(true, sev)$l.shift,
    sshift = epi.ccc(true, sev)$s.shift,
    r = cor(ImageJ, sev)
  ) 
```


## Agreement interval

```{r}
library(epiR)
library(AgreementInterval)
dat <- sad1 %>%
  filter(Rater == 37) %>%
  select(true, Aided, Unaided)
ag1A <- ai(x = dat$true, y = dat$Aided, clin.limit = c(-10, 10))
ag1A$intervalEst$`95LL`[3]
ag1A$intervalEst$`95UL`[3]
ag1A$alpha.cl
ag1A$tolProb.cl

ag1U <- ai(x = dat$true, y = dat$Unaided, clin.limit = c(-10, 10))
ag1U$intervalEst$`95LL`[3]
ag1U$intervalEst$`95UL`[3]
ag1U$alpha.cl
```


```{r}
gain <- dat_ccc %>%
  ungroup() %>%
  select(Laboratory, Rater, type, ccc_est) %>%
  group_by(type) %>%
  mutate(row = row_number()) %>%
  tidyr::pivot_wider(names_from = type, values_from = ccc_est) %>%
  mutate(diff = Aided - Unaided)
```



```{r}
theme_set(theme_minimal_grid())
gain %>%
  ggplot(aes(Laboratory, diff)) +
  geom_violin(outlier.colour = NA) +
  geom_hline(yintercept = 0) +
  geom_jitter(width = 0.05, shape =1) +
  theme_minimal_grid()
```



# Effect-size

```{r}
library(effectsize)
gainA <- gain %>%
  filter(Laboratory == "A")
hedges_g("Aided", "Unaided", data = gainA, correction = T, paired = TRUE)
```

```{r }
library(cowplot)
library(hrbrthemes)
library(viridis)
theme_set(theme_minimal_grid(font_size = 7))

ccc1 <- dat_ccc %>%
  ggplot(aes(cb, r, color = ccc_est, shape = type, label = Rater)) +
  theme_minimal_grid(font_size =12) +
  theme(legend.position = "top",
        legend.text=element_text(size=rel(0.6))) +
   ylim(0.35, 1)+
  geom_point(size = 3, alpha = 0.9) +
  # geom_text(check_overlap = TRUE)+
  scale_color_gsea(reverse = T) +
  facet_wrap(~Laboratory, ncol =4) +
  labs(
    color = "ﾏ…", shape = "Method", x = "Generalized bias (Cb)",
    y = "Precision (r)"
  )
```


```{r}
ccc2 <- dat_ccc %>%
  ggplot(aes(reorder(type, ccc_est), ccc_est, fill = ccc_est, group = Rater)) +
  geom_line(color = "gray40", position = position_dodge(width = 0.2)) +
  geom_point(alpha = 0.7, size = 3, shape = 21, position = position_dodge(width = 0.2)) +
  theme_minimal_grid() +
  labs(
    y = "Concordance coefficient (ﾏ…) ",
    x = "Assessment type",
    fill = "ﾏ…"
  ) +
  ylim(0.25, 1)+
  theme(legend.position = "none")+
  scale_fill_gsea(reverse = T)+
  facet_wrap(~Laboratory, ncol =4) 

````


```{r}
ccc1 / ccc2 +
  plot_layout(guides = 'auto') + plot_annotation(tag_levels = "A")
ggsave("figs/Fig_CCC.png", width =9, height =7)

```


## glmmTMB

```{r}
library(glmmTMB)


mix2 <- glmmTMB(cb ~ type * Laboratory + (1 | Rater), dat_ccc_true, beta_family(link = "logit"), REML = F)
car::Anova(mix2)



summary(mix2)
library(ggeffects)
df <- data.frame(ggpredict(mix2, terms = c("Laboratory", "type")))
df
library(emmeans)
x <- emmeans(mix2, ~ type | Laboratory, transform = "response")
library(multcomp)
cld(x)
emmip(mix2,  Laboratory ~ type)
plot(x, by = "Laboratory")
```

### R2 statistics

```{r}

cor(model.response(model.frame(mix2)),predict(mix2,type="response"))^2
1-var(residuals(mix2))/var(model.response(model.frame(mix2)))

```

## Influence analysis

```{r}
library(influence.ME)
influence(mix2, "Rater")

```



### testing overdispersion

```{r}
overdisp_fun <- function(model) {
    rdf <- df.residual(model)
    rp <- residuals(model,type="pearson")
    Pearson.chisq <- sum(rp^2)
    prat <- Pearson.chisq/rdf
    pval <- pchisq(Pearson.chisq, df=rdf, lower.tail=FALSE)
    c(chisq=Pearson.chisq,ratio=prat,rdf=rdf,p=pval)
}
overdisp_fun(mix2)

```


### model fit

```{r}
library(broom.mixed)
aa <- augment(mix2, data = dat_ccc)
gg2 <- (ggplot(aa, aes(.fitted, .resid))
+ geom_line(aes(group = Rater), colour = "gray")
  + geom_point(aes(colour = type, shape = Laboratory))
  + geom_smooth()
)
gg2

aa$.fitted0 <- predict(mix2, newdata = transform(dat_ccc, Rater = NA), type = "response")
aa$.resid0 <- dat_ccc$ccc_est - aa$.fitted0
gg3 <- (ggplot(aa, aes(.fitted0, .resid0))
+ geom_line(aes(group = Rater), colour = "gray")
  + geom_point(aes(colour = Laboratory, shape = type))
  + geom_smooth()
)
gg3
lme4:::dotplot.ranef.mer(ranef(mix2)$cond)
```

## Figure CCC estimates

````{r}
df$group <- factor(df$group, levels = c("Unaided", "Aided"))

dat_ccc$type <- factor(dat_ccc$type, levels = c("Unaided", "Aided"))

df %>%
  dplyr::select(group, x, predicted, conf.low, conf.high)  %>%
  ggplot(aes(x = x, y = predicted, color = group)) +

  geom_violin(
    data = dat_ccc, aes(Laboratory, ccc_est, fill = type),
    position = position_dodge(width = 0.5), alpha = 0.3,
    color = NA
  ) +
  geom_point(position = position_dodge(width = 0.5), size = 2) +
  geom_errorbar(aes(ymin = conf.low, ymax =  conf.high),
    width = 0.1,
    position = position_dodge(width = 0.5), size = 0.8
  ) +
  geom_text(
    aes(label = round(predicted, 2), predicted = predicted + 0.05),
    position = position_dodge(1.2),
    vjust = 0
  ) +

  scale_fill_startrek() +
  scale_color_startrek() +
  theme_minimal_grid(font_size = 10) +
  labs(
    x = "Laboratory", y = "Overall concordance (ﾏ…)",
    fill = "Assessment", color = NA
  ) +
  theme(legend.position = "bottom") +
  guides(color = FALSE) +
  ylim(0.3, 1) +
  ggsave("figs/estimates_overall_concordace.png", width = 5, height = 3.5)
```




```{r fig.height=3, fig.width=5}
library(cowplot)
library(gghalves)
library(ggbeeswarm)
library(viridis)
library(ggsci)
```

## Interrater reliability

Two methods were used here. The overall concordance coefficient and the intra-class correlation coefficient.


### Aided

```{r}
library(irr)
library(epiR)
library(dplyr)
sad_aid <- sad1 %>% 
  dplyr::select(Leaf, Rater, Aided) %>% 
    spread(Rater, Aided, 2:3) %>% 
  dplyr::select(-1) %>% 
   data.matrix()

sad_occc_aid <- epi.occc(sad_aid, na.rm = FALSE, pairs = TRUE)
sad_icc_aid <- icc(sad_aid, model = "twoway", unit = "single", type = "agreement")
sad_occc_aid$occc
sad_icc_aid$value
sad_icc_aid$lbound
sad_icc_aid$ubound

# install.packages("psych")
library(psych)
i <- ICC(sad_aid)
i

```


### Unaided

```{r}
sad_noaid <- sad1 %>% 
  dplyr::select(Leaf, Rater, Unaided) %>% 
    spread(Rater, Unaided, 2:3) %>% 
   dplyr::select(-1) %>% 
   data.matrix()

sad_occc_noaid <- epi.occc(sad_noaid, na.rm = FALSE, pairs = TRUE)
sad_icc_noaid <- icc(sad_noaid, model = "twoway", unit = "single", type = "agreement")
sad_occc_noaid$occc
sad_icc_noaid$value
sad_icc_noaid$lbound
sad_icc_noaid$ubound

i <- ICC(sad_noaid)
i



```


## Laboratory A

```{r}
sad_aid_A <- sad1 %>% 
  filter(Laboratory == "A") %>% 
  dplyr::select(Leaf, Rater, Aided) %>% 
    spread(Rater, Aided, 2:3) %>% 
   dplyr::select(-1) %>% 
   data.matrix()

sad_occc_aid_A <- epi.occc(sad_aid_A, na.rm = FALSE, pairs = TRUE)
sad_icc_aid_A <- icc(sad_aid_A, model = "oneway", unit = "single", type = "agreement")
sad_occc_aid_A$occc
sad_icc_aid_A$value
sad_icc_aid_A$lbound
sad_icc_aid_A$ubound

sad_aid_A <- sad1 %>% 
  filter(Laboratory == "A") %>% 
  dplyr::select(Leaf, Rater, Unaided) %>% 
    spread(Rater, Unaided, 2:3) %>%
  dplyr::select(-1) %>% 
   data.matrix()

sad_occc_aid_A <- epi.occc(sad_aid_A, na.rm = FALSE, pairs = TRUE)
sad_icc_aid_A <- icc(sad_aid_A, model = "oneway", unit = "single", type = "agreement")
sad_occc_aid_A$occc
sad_icc_aid_A$value
sad_icc_aid_A$lbound
sad_icc_aid_A$ubound

i <- ICC(sad_aid_A)
i$summary


```



## Laboratory B

```{r}
sad_aid_B <- sad1 %>% 
  filter(Laboratory == "B") %>% 
  dplyr::select(Leaf, Rater, Unaided) %>% 
    spread(Rater, Unaided, 2:3) %>% 
   dplyr::select(-1) %>% 
   data.matrix()

sad_occc_aid_B <- epi.occc(sad_aid_B, na.rm = FALSE, pairs = TRUE)
sad_icc_aid_B <- icc(sad_aid_B, model = "oneway", unit = "single", type = "agreement")
sad_occc_aid_B$occc
sad_icc_aid_B$value
sad_icc_aid_B$lbound
sad_icc_aid_B$ubound

i <- ICC(sad_aid_B)
i$summary
i




```



## Laboratory C

```{r}
sad_aid_C <- sad1 %>% 
  filter(Laboratory == "C") %>% 
  dplyr::select(Leaf, Rater, Aided) %>% 
    spread(Rater, Aided, 2:3) %>%
  dplyr::select(-1) %>% 
  
   data.matrix()

sad_occc_aid_C <- epi.occc(sad_aid_C, na.rm = FALSE, pairs = TRUE)
sad_icc_aid_C <- icc(sad_aid_C, model = "oneway", unit = "single", type = "agreement")
sad_occc_aid_C$occc
sad_icc_aid_C$value
sad_icc_aid_C$lbound
sad_icc_aid_C$ubound

i <- ICC(sad_aid_C)
i$summary
i

```



## Laboratory D

```{r}
sad_aid_D <- sad1 %>% 
  filter(Laboratory == "D") %>% 
  dplyr::select(Leaf, Rater, Unaided) %>% 
    spread(Rater, Unaided, 2:3) %>% 
  dplyr::select(-1) %>% 
   data.matrix()

sad_occc_aid_D <- epi.occc(sad_aid_D, na.rm = FALSE, pairs = TRUE)
sad_icc_aid_D <- icc(sad_aid_D, model = "twoway", unit = "single", type = "agreement")
sad_occc_aid_D$occc
sad_icc_aid_D$value
sad_icc_aid_D$lbound
sad_icc_aid_D$ubound

i <- ICC(sad_aid_D)
i$summary
i

```

```{r}
library(rptR)
data(BeetlesBody)
str(BeetlesBody)

rpt(BodyL ~ (1 | Population), grname = "Population", data = BeetlesBody, datatype = "Gaussian", 
    nboot = 0, npermut = 0)
rpt(Unaided ~ (1 | Laboratory), grname = "Laboratory", data = sad1, datatype = "Gaussian", 
    nboot = 0, npermut = 0)

dat <- BeetlesBody

```

